Tabular Constraint Learning

### 2016-04-26 Paper/ECAI/tabular.tex
Cleanup and approach

Given these novel aspects, we conclude that understanding and learning constraints in tabular data is a new and challenging problem setting.
Futhermore, it is not only challenging for a machine but for a human as well.

@@

\subsection{Constraints}
A \template is a triple \textit{(\CName, \CSignature, \CFunction)}.
Let us elaborate on this:
\begin{itemize}
\item
\textit{\CName}  specifies the syntactic form of the constraint $c(A_1, ...,A_n)$, that is, the name of the constraint $c$ together
with $n$ arguments $A_i$. Thus a constraint $c$ is viewed as a relation or predicate of arity $n$ in first order logic.
% the list of its variables $v_1,\dots,v_n$.  In ILP terminology, it is known as vocabulary.
\item the \textit{\CSignature} constrains the arguments $A_i$ of the constraint, that is, the types of the arguments, together
with possible further restrictions using properties of the arguments $A_i$ such as their length.  For example, the signature can restrict the types of the arguments
to be vectors of integers and require that  the length of all arguments be equal.  In terms of logical and relational learning, this is known as the {\em bias} of the learner,
it specifies when the constraint is well-formed.
  %The constraints act on properties or group meta-information, not on the actual group content. In ILP, it is known as bias,
  \item \textit{\CFunction} is the actual definition of the constraint that specifies when the constraint holds, in practice this will be a function that can be called when
the arguments are full instantiated to decide whether the constraint is satisfied or not. In logical and relational learning this is known as the background knowledge, which provides the definition of the predicate.
\end{itemize}

@@

\luc{Delete from here}
\luc{ADD/REFER TO EXAMPLE}

Let us introduce \template instantiation syntax. Let $S$ be a mapping from variables to the subgroups of \groups and $t$ be a \template, then $t^S$ is the template, in which all variables in all constrainst in \CSignature and \CFunction are instantiated with the corresponding subgroups from $S$. We refer to $t^S$ as a \textit{constraint} and to the instantiated \CSignature (\CFunction) as $\text{\CSignature}^S$ ($\text{\CFunction}^S$). Throughout the work we refer as \textit{find constraints} to finding all constraints that hold.

Let us now define what it means for a constraint from \template to hold in general. Let $t$ be a \template, $S$ be a mapping from variables to the subgroups of \groups, and $C$ be the constraint $t^S$, then $C$ \textit{holds} iff all constraints in $\text{\CSignature}^S$ and $\text{\CFunction}^S$ of $C$ hold.
\sergey{moved from formalization END}

In the previous section we introduced the problem of tabular constraint learning informally using the example in Figure \ref{fig:main_example}. Here we formalize the statement in terms of \template and group assignments as follows:

\begin{minipage}[c]{14em}
  \vspace{5pt}
  \begin{tabular}{ll}
    \multicolumn{2}{l}{{\textbf{Tabular Constraint Learning Problem}}}\\
    \vspace{-4pt}
    &\\
    \textbf{Given:}& the set of all groups $\groups$ and of \template $\constraints$\\
    \textbf{Find:}&  all constraints $C$ over \groups for each template $t$ in \constraints \\
  \end{tabular}
  \vspace{6pt}
\end{minipage}
\luc{To here}

@@

\subsection{Generality ordering}
A constraint~$c_1$ is a special case of another constraint~$c_2$ iff whenever $c_1$ is true, $c_2$ must also be true.
We consider $c_1$ to be more specific than $c_2$ or $c_2$ to be more general than $c_1$.
A constraint template~$s_1$ is more specific than a template~$s_2$ iff a constraint applying $s_1$ to a set of subgroups is always more specific than a constraint applying $s_2$ to (part of) the same set.

@@

\subsection{Candidate group generation}
$\generategroups(\textit{Constraint,GroupSet,Solutions})$ is the function generating tuples of groups (group-assignments~$A$) that may contains subgroups satisfying the constraint.
The goal of this step is to prune out impossible groups from the beginning by looking at their properties rather than their actual content (\CSignature vs \CFunction).

@@

\paragraph{Example}
\ecrank{v_r}{v_x} will require groups assigned to $v_r$ to be $\integer$, groups assigned to $v_x$ to be $\discrete$ (i.e. $\integer$ or $\textual$) and only allows assignments in which groups assigned to both variables have the same length.

\subsection{Subgroup satisfaction search}
$\findassignment(t,A,C_{solutions})$ finds, for all assignments~$a = (G_1, ..., G_n)$ in $A$, the subgroups $G_i' \subseteq G_i$ such that $t(G_1', ..., G_n')$ is satisfied.
For every \template~$t$ an implementation (declarative or imperative) need to be provided that finds valid subgroups given the assignments.
 assignments, given set of tuples each containing a candidate group for every variable in~$t$.

\paragraph{Example}
Consider a candidate assignment $G_x, G_y$ associated with the variables $v_x,v_y$ of \ecrank{v_y}{v_x}, then \findassignment selects single vectors $g_y \in G_y, g_x \in G_x$ such that \ecrank{g_y}{g_x} is true, i.e. it searches for a mapping $S$ where $v_x$ ($v_y$) must be mapped to a subgroup of $G_x$ ($G_y$).
For example, in Figure~\ref{fig:main_example} the group $G = \range{T_1}{\rangeall}{\rangeto{3}{8}}$ can serve as both $G_x$ and $G_y$.
Then \findassignment could select $g_x$ to be $\range{T_1}{\rangeall}{7}$ and $g_y$ to be $\range{T_1}{\rangeall}{8}$ which forms a valid solution.
\\\\
For some constraints (most notably aggregates) there may be multiple overlapping subsets of a given group~$G$ that satisfy the constraint.
We chose to omit subsets that are fully contained within a larger subset since this can lead to overfitting.
If the returned subsets are too large and accidentally contain unrelated vectors, the user can split such a group, disallowing.

\subsection{Implementation note} Essentially for each \template both \generategroups and \findassignment are separate constraint satisfaction problems. Hence, it is natural to solve them using declarative solvers. Even though each is a separate constraint problem, they are variations of each other and can be modeled using similar techniques. It also makes an extension of the system easy, we can solve new variations by adding, removing or modifying constraints from a similar constraint satisfaction problem. Furthermore, declarative languages such as ASP \cite{whaisasp} and Minizinc \cite{minizinc} provide primitives that make modeling transparent and generic.

Our system internally supports ASP (using Clingo 4.5.4 \cite{clingo}), Minizinc (Gecode-backend 2.0.2 \cite{minizinc}) and a native Python CSP solver \cite{python_constraint}. All the constraints mentioned in the paper can be run purely using the internal Python engine without any external software. Future versions of the system will provide user interfaces to the ASP, Minizinc and Python-Constraint languages to allow users to add new constraints in a declarative way.

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.9\linewidth]{figures/constraint_dependency.png}
  \caption{Constraint Learning Order. The solid arrows indicate a specificity order, i.e., \textit{permutation} $\rightarrow$ \textit{series} means that the series constraint is more specific than permutation. The dashed arrows indicate an inverse construction order, \textit{project} $\dashrightarrow$ \textit{aggregates} means the project constraint is more specific than aggregates. \sergey{Samuel,  can you give an explanation why we keep both arrow and how it is internally motivated?}}
  \label{fig:learning_order}
\end{figure}

\sergey{Table should take into account our new notation and balance between formality and intuition, heh}

@@

      & $v_{fk}$ and $v_{pk}$ are both $\discrete$; variables $\{v_{fk}, v_{r}\}$ and $\{v_{pk}, v_{val}\}$ within the same set have the same \plength, \ptable and \por; $v_{r}$ and~$v_{val}$ have the same type; and \ecfkey{v_{fk}}{v_{pk}}.

@@

      & Variables $\{v_{r}, v_{1}, v_{fk}\}$ are $\numeric$, variables $\{v_{pk}, v_{val}\}$ are $\discrete$ and within both sets all variables have the same \plength, \ptable and \por; also \ecfkey{v_{fk}}{v_{pk}}.

@@

      & Variables $\{v_{r}, v_{1}, v_{2}\}$ are all $\numeric$ and have the same $\plength$

@@

      & Variables $\{v_{r}, \mathbf{v_x}\}$ all have the same $\plength$, $\por$, $\ptable$ and $\ptype$; $\mathbf{v_x}$ contains at least~2 vectors

@@

      & Variables $\{v_{r}, v_{pos}, v_{neg}\}$ are all $\numeric$ and all have the same $\plength$, which is at least $2$

@@

    \ecsumc{v_r}{\mathbf{v_x}}

@@

    \ecsumr{v_r}{\mathbf{v_x}}

@@

    \ecsumif{v_r}{v_{fk}}{v_{pk}}{v_{val}}
      & $v_{fk}, v_{pk}$ are $\discrete$; $v_{r}, v_{val}$ are $\numeric$; within the sets $\{v_{val}, v_{fk}\}$ and $\{v_{pk}, v_{r}\}$ variables have the same $\plength$ and $\por$; $v_{fk}$ and $v_{val}$ have the same $\ptable$; $v_{fk}$ and $v_{pk}$ must have different $\ptable$s but the same $\ptype$; and \ecalldiff{v_{pk}}

@@

      & Variables $\{v_r, v_1, v_2\}$ are all $\numeric$; $\plength(v_{1}) = \plength(v_{2}) \geq 2$; and $\prows(v_{r}) = \pcols(v_{r}) = 1$

@@

\samuel{Satisfy signature for group assignment: find groups such that there exists a subgroup which satisfies the signature}

@@

\begin{figure}
  {\small
    \begin{align*}
      & SERIES(\range{T_{1}}{\rangeall}{1}) \\
%
      & \ecrank{\range{T_{1}}{\rangeall}{8}}{\range{T_{1}}{\rangeall}{7}} \\
%
      & \ecsumc{\range{T_{2}}{1}{\rangeall}}{\range{T_{1}}{\rangeall}{\rangeto{3}{7}}} \\
%
      & \ecsumc{\range{T_{6}}{\rangeall}{2}}{\range{T_{1}}{\rangeall}{\rangeto{3}{6}}} \\
%
      & \ecsumr{\range{T_{1}}{\rangeall}{7}}{\range{T_{1}}{\rangeall}{\rangeto{3}{6}}} \\
%
      & \ecaggc{AVERAGE}{\range{T_{2}}{2}{\rangeall}}{\range{T_{1}}{\rangeall}{\rangeto{3}{7}}} \\
%
      & \ecaggc{MAX}{\range{T_{2}}{3}{\rangeall}}{\range{T_{1}}{\rangeall}{\rangeto{3}{7}}} \\
%
      & \ecaggc{MIN}{\range{T_{2}}{4}{\rangeall}}{\range{T_{1}}{\rangeall}{\rangeto{3}{7}}} \\
%
      & \ecaggif{SUM}{\range{T_{1}}{\rangeall}{10}}{\range{T_{5}}{\rangeall}{1}}{\range{T_{1}}{\rangeall}{2}}{\range{T_{5}}{\rangeall}{2}} \\
%
      & \ecaggif{MAX}{\range{T_{1}}{\rangeall}{11}}{\range{T_{5}}{\rangeall}{1}}{\range{T_{1}}{\rangeall}{2}}{\range{T_{5}}{\rangeall}{2}} \\
%
      & \eclookup{\range{T_{4}}{\rangeall}{3}}{\range{T_{4}}{\rangeall}{2}}{\range{T_{1}}{\rangeall}{1}}{\range{T_{1}}{\rangeall}{2}} \\
%
      & \range{T_{6}}{\rangeall}{4} = PREV(\range{T_{6}}{\rangeall}{4}) + \range{T_{6}}{\rangeall}{2} - \range{T_{6}}{\rangeall}{3}
    \end{align*}
  }
  \caption{Expected constraints in the case study \sergey{in Figure \ref{fig:main_example}; some more explanation needed, not self explanatory}}
  \label{fig:sol_example}
\end{figure}
\sergey{Samuel, hint, don't put label before caption, it can't resolve it sometimes}

@@

\paragraph{Dependencies}
In order for the algorithm to run efficiently it is crucial to use dependencies and find constraint incrementally whenever possible.
This avoids some of the explosion of combinations for constraints that have variables.
For example, using foreign keys as a base constraint to find conditional aggregates reduces the running time for the case study from about 3 seconds to below 1 second.
Unfortunately, this assumption is sometimes too strong, when users are interested in aggregates for only some of the keys that are present in the data.

@@

conclusions 
points: 1) can be a base for an actual plugin or a function in excel 2) novel problem and challenge for systems and constraint solvers 3) can be part of the complicated pipeline togehter with the header detection

>>>>

Given these novel aspects, we conclude that understanding and learning constraints in tabular data is a new and challenging problem setting.
Furthermore, it is not only challenging for a machine but for a human as well.

@@

\subsection{Constraints}
A \template is a triple \textit{(\CName, \CSignature, \CFunction)}.
Let us elaborate on this:
\begin{itemize}
\item
\textit{\CName}  specifies the syntactic form of the constraint $c(A_1, ...,A_n)$, that is, the name of the constraint $c$ together
with $n$ arguments $A_i$. Thus a constraint $c$ is viewed as a relation or predicate of arity $n$ in first order logic.
\samuel{Or a function}
% the list of its variables $v_1,\dots,v_n$.  In ILP terminology, it is known as vocabulary.
\item the \textit{\CSignature} constrains the arguments $A_i$ of the constraint, that is, the types of the arguments, together
with possible further restrictions using properties of the arguments $A_i$ such as their length.  For example, the signature can restrict the types of the arguments
to be vectors of integers and require that  the length of all arguments be equal.  In terms of logical and relational learning, this is known as the {\em bias} of the learner,
it specifies when the constraint is well-formed.
  %The constraints act on properties or group meta-information, not on the actual group content. In ILP, it is known as bias,
  \item \textit{\CFunction} is the actual definition of the constraint that specifies when the constraint holds, in practice this will be a function that can be called when
the arguments are full instantiated to decide whether the constraint is satisfied or not. In logical and relational learning this is known as the background knowledge, which provides the definition of the predicate.
\end{itemize}

@@

% \luc{Delete from here}
% \luc{ADD/REFER TO EXAMPLE}

% Let us introduce \template instantiation syntax. Let $S$ be a mapping from variables to the subgroups of \groups and $t$ be a \template, then $t^S$ is the template, in which all variables in all constrainst in \CSignature and \CFunction are instantiated with the corresponding subgroups from $S$. We refer to $t^S$ as a \textit{constraint} and to the instantiated \CSignature (\CFunction) as $\text{\CSignature}^S$ ($\text{\CFunction}^S$). Throughout the work we refer as \textit{find constraints} to finding all constraints that hold.

% Let us now define what it means for a constraint from \template to hold in general. Let $t$ be a \template, $S$ be a mapping from variables to the subgroups of \groups, and $C$ be the constraint $t^S$, then $C$ \textit{holds} iff all constraints in $\text{\CSignature}^S$ and $\text{\CFunction}^S$ of $C$ hold.
% \sergey{moved from formalization END}

% In the previous section we introduced the problem of tabular constraint learning informally using the example in Figure \ref{fig:main_example}. Here we formalize the statement in terms of \template and group assignments as follows:

% \begin{minipage}[c]{14em}
%   \vspace{5pt}
%   \begin{tabular}{ll}
%     \multicolumn{2}{l}{{\textbf{Tabular Constraint Learning Problem}}}\\
%     \vspace{-4pt}
%     &\\
%     \textbf{Given:}& the set of all groups $\groups$ and of \template $\constraints$\\
%     \textbf{Find:}&  all constraints $C$ over \groups for each template $t$ in \constraints \\
%   \end{tabular}
%   \vspace{6pt}
% \end{minipage}
% \luc{To here}

\samuel{Not reworked yet from here ---}

@@

\subsubsection{Generality ordering}

\begin{figure}[tbh]
  \centering
  \includegraphics[width=0.9\linewidth]{figures/constraint_dependency.png}
  \caption{Constraint Learning Order. The solid arrows points from more general to more specific constraints templates (e.g. \textit{all-different} is more general than \textit{permutation}).}
  \label{fig:learning_order}
\end{figure}

A constraint~$c_1$ is a special case of another constraint~$c_2$ iff whenever $c_1$ is true, $c_2$ must also be true.
We consider $c_1$ to be more specific than $c_2$ or $c_2$ to be more general than $c_1$.
A constraint template~$s_1$ is more specific than a template~$s_2$ iff a constraint applying $s_1$ to a set of subgroups is always more specific than a constraint applying $s_2$ to (part of) the same set.

@@

\subsubsection{Candidate group generation}
$\generategroups(\textit{Constraint,GroupSet,Solutions})$ is the function generating tuples of groups (group-assignments~$A$) that may contains subgroups satisfying the constraint.
The goal of this step is to prune out impossible groups from the beginning by looking at their properties rather than their actual content (\CSignature vs \CFunction).

@@

\paragraph{Example}
\ecrank{v_r}{v_x} will require groups assigned to $v_r$ to be $\integer$, groups assigned to $v_x$ to be $\discrete$ (i.e. $\integer$ or $\textual$) and only allows assignments in which groups assigned to both arguments have the same length.

\subsubsection{Subgroup satisfaction search}
$\findassignment(t,A,C_{solutions})$ finds, for all assignments~$a = (G_1, ..., G_n)$ in $A$, the subgroups $G_i' \subseteq G_i$ such that the corresponding constraint $t(G_1', ..., G_n')$ is satisfied.
For every \template~$t$ an implementation (declarative or imperative) needs to be provided that finds valid subgroups given the assignments.

\paragraph{Example}
Consider a group assignment $G_x, G_y$ associated with the arguments $v_x,v_y$ of \ecrank{v_y}{v_x}, then \findassignment selects single vectors $V_y \in G_y, V_x \in G_x$ such that \ecrank{V_y}{V_x} is true.
For example, in Figure~\ref{fig:main_example} the group $G = \range{T_1}{\rangeall}{\rangeto{3}{8}}$ can serve as both $G_x$ and $G_y$.
Then \findassignment could select $V_x$ to be $\range{T_1}{\rangeall}{7}$ and $V_y$ to be $\range{T_1}{\rangeall}{8}$ since \ecrank{\range{T_1}{\rangeall}{7}}{\range{T_1}{\rangeall}{8}} is satisfied in the data.
\\\\
For some constraint templates (most notably aggregates) there may be multiple (overlapping) subgroups of a given group~$G$ for which the template satisfied.
In this case we choose to omit those subgroups that are fully contained within a larger subgroup since this can lead to over-fitting.
If the returned subsets are too large and accidentally include unrelated vectors the user can split such a group.

\subsection{Implementation note}
For each \template, both \generategroups and \findassignment are can be seen as separate constraint satisfaction problems.
Hence, it is natural to solve them using declarative solvers.
Even though each of these problems differ from each other, they are variations that can be modeled using similar techniques.
This also makes it easy to extend the implementation as templates can be easily added (or removed).
Furthermore, declarative languages such as, for example, ASP \cite{whaisasp} and Minizinc \cite{minizinc} provide primitives that make modeling transparent and generic.

Our system internally supports ASP (using Clingo 4.5.4 \cite{clingo}), Minizinc (Gecode-backend 2.0.2 \cite{minizinc}) and uses a native Python CSP solver \cite{python_constraint} for \generategroups.
All the constraints mentioned in the paper can be run purely using the internal Python engine without any external software.
Future versions of the system will provide user interfaces to some of these constraint languages (e.g. ASP and Minizinc) to allow users to specify solving procedures for new constraint templates in a declarative way.

@@

@@

      & $v_{fk}$ and $v_{pk}$ are both $\discrete$; arguments $\{v_{fk}, v_{r}\}$ and $\{v_{pk}, v_{val}\}$ within the same set have the same \plength, \ptable and \por; $v_{r}$ and~$v_{val}$ have the same type; and \ecfkey{v_{fk}}{v_{pk}}.

@@

      & Arguments $\{v_{r}, v_{1}, v_{fk}\}$ are $\numeric$, arguments $\{v_{pk}, v_{val}\}$ are $\discrete$ and within both sets all arguments have the same \plength, \ptable and \por; also \ecfkey{v_{fk}}{v_{pk}}.

@@

      & Arguments $\{v_{r}, v_{1}, v_{2}\}$ are all $\numeric$ and have the same $\plength$

@@

      & Arguments $\{v_{r}, \mathbf{v_x}\}$ all have the same $\plength$, $\por$, $\ptable$ and $\ptype$; $\mathbf{v_x}$ contains at least~2 vectors; and $v_r = \mathit{SUM}(\mathbf{v_x}, \por(\mathbf{v_x}))$

@@

      & Arguments $\{v_{r}, v_{pos}, v_{neg}\}$ are all $\numeric$ and all have the same $\plength$, which is at least $2$

@@

    $\ecsumc{v_r}{\mathbf{v_x}}^\dagger$

@@

    $\ecsumr{v_r}{\mathbf{v_x}}^\dagger$

@@

    $\ecsumif{v_r}{v_{fk}}{v_{pk}}{v_{val}}^\dagger$
      & $v_{fk}, v_{pk}$ are $\discrete$; $v_{r}, v_{val}$ are $\numeric$; within the sets $\{v_{val}, v_{fk}\}$ and $\{v_{pk}, v_{r}\}$ arguments have the same $\plength$ and $\por$; $v_{fk}$ and $v_{val}$ have the same $\ptable$; $v_{fk}$ and $v_{pk}$ must have different $\ptable$s but the same $\ptype$; and \ecalldiff{v_{pk}}

@@

      & Arguments $\{v_r, v_1, v_2\}$ are all $\numeric$; $\plength(v_{1}) = \plength(v_{2}) \geq 2$; and $\prows(v_{r}) = \pcols(v_{r}) = 1$

@@

Table~\ref{table:constraints} shows all constraint templates currently supported by our implementation.
Their dependencies are reflected in their \CSignature and shown in Figure~\ref{fig:learning_order}.
These constraints have been selected based on the most-used Excel functions as well as their occurrence in various example spreadsheets we observed.

@@

\begin{figure}
  {\small
    \begin{align*}
      & SERIES(\range{T_{1}}{\rangeall}{1}) \\
%
      & \ecrank{\range{T_{1}}{\rangeall}{8}}{\range{T_{1}}{\rangeall}{7}} \\
%
      & \ecsumc{\range{T_{2}}{1}{\rangeall}}{\range{T_{1}}{\rangeall}{\rangeto{3}{7}}} \\
%
      & \ecsumc{\range{T_{6}}{\rangeall}{2}}{\range{T_{1}}{\rangeall}{\rangeto{3}{6}}} \\
%
      & \ecsumr{\range{T_{1}}{\rangeall}{7}}{\range{T_{1}}{\rangeall}{\rangeto{3}{6}}} \\
%
      & \ecaggc{AVERAGE}{\range{T_{2}}{2}{\rangeall}}{\range{T_{1}}{\rangeall}{\rangeto{3}{7}}} \\
%
      & \ecaggc{MAX}{\range{T_{2}}{3}{\rangeall}}{\range{T_{1}}{\rangeall}{\rangeto{3}{7}}} \\
%
      & \ecaggc{MIN}{\range{T_{2}}{4}{\rangeall}}{\range{T_{1}}{\rangeall}{\rangeto{3}{7}}} \\
%
      & \ecaggif{SUM}{\range{T_{1}}{\rangeall}{10}}{\range{T_{5}}{\rangeall}{1}}{\range{T_{1}}{\rangeall}{2}}{\range{T_{5}}{\rangeall}{2}} \\
%
      & \ecaggif{MAX}{\range{T_{1}}{\rangeall}{11}}{\range{T_{5}}{\rangeall}{1}}{\range{T_{1}}{\rangeall}{2}}{\range{T_{5}}{\rangeall}{2}} \\
%
      & \eclookup{\range{T_{4}}{\rangeall}{3}}{\range{T_{4}}{\rangeall}{2}}{\range{T_{1}}{\rangeall}{1}}{\range{T_{1}}{\rangeall}{2}} \\
%
      & \range{T_{6}}{\rangeall}{4} = PREV(\range{T_{6}}{\rangeall}{4}) + \range{T_{6}}{\rangeall}{2} - \range{T_{6}}{\rangeall}{3}
    \end{align*}
  }
  \caption{Constraints that are satisfied in the case study (Figure~\ref{fig:main_example}) and expected to be found by our implementation. Functional constraint are omitted.}
  \label{fig:sol_example}
\end{figure}

@@

\paragraph{Dependencies}
In order for the algorithm to run efficiently it is crucial to use dependencies and find constraint incrementally whenever possible.
This avoids some of the explosion of combinations for constraints that have many arguments.
For example, using foreign keys as a base constraint to find conditional aggregates reduces the running time for the case study from about 3 seconds to below 1 second.
Unfortunately, this assumption is sometimes too strong, when users are interested in aggregates for only some of the keys that are present in the data.

@@

conclusions 
% points: 1) can be a base for an actual plugin or a function in excel 2) novel problem and challenge for systems and constraint solvers 3) can be part of the complicated pipeline togehter with the header detection
Our goal was to automatically identify constraints that hold in a spreadsheet.
We have presented and evaluated an approach that is able to learn a large set constraints from CSV data.

fututre work
